\thetitle

### 2021-05-11 paper/paper.tex
minor

\begin{abstract}
  % teilw. von IJPR paper uebernommen
  An essential task in manufacturing planning and control is to determine when to release orders to
  the shop floor. One key parameter is the lead time which is the planned time that elapses between
  the release of an order and its completion. Lead times are usually determined based on the
  measured duration orders take to traverse the production system, i.e.\@ the flow times.
  Traditional order release models assume static lead times, although it has been shown that they
  should be set dynamically to be able to react to the dynamic operational characteristics of
  production system. Therefore, we present an order release model which sets lead times dynamically
  by using an reinforcement learning approach. This algorithm is designed especially for
  applications with high variability and periodic feedback to the agent. Therefore, this paper aims
  at providing a proof-of-concept for the proposed algorithm. Therefore, we compare our method on a
  three-stage flow-shop simulation model not only to static order release techniques, but also to
  the commonly used deep Q-Learning algorithm. The results show that both reinforcement learning
  agents have room for improvement for queuing systems with low variability, that our proposed
  method usually outperforms deep Q-Learning and finally for systems with high variability that the
  proposed reinforcement learning algorithm performs very well.
  %
  % We use a  to compare the algorithm
  % to % and show that our approach outperforms
  % well-known order release mechanisms. We show that in the current version our proposed model using
  % reinforcement learning outperforms some, but not all other tested approaches.
  % EVTL: especially for scenarios with...
  \keywords{operations research, production planning, order release, machine learning, reinforcement
    learning}
\end{abstract}

@@

Therefore, in the future we plan to develop \ARA{} further to a actor-critic state-of-the-art
reinforcement learning algorithm. We hypothesise that due to the more correct state value
estimations of \ARA{} as compared to deep Q-Learning, cf. \citet{schneckenreither2020average}, the
critic will provide a better feedback of the value function update to the actor. This should lead to
better policies than with standard actor-critic algorithms, e.g. A3C~\citep{mnih2016asynchronous}.
%
Furthermore, one limitation of this proof-of-concept study is that due to the computational
complexity we restricted our scope to flow-shop production systems only. In subsequent studies we
plan to test the algorithms on job-shop queuing systems as well.
%
Additionally, we want to exploit hierarchical production
planning~\citep{schneeweibeta1995hierarchical} by implementing agents on different hierarchical
levels which can bargain with each other. For instance, one agent might be responsible for medium
term planning order release decision at the top level, while another agent concentrates on
short-term scheduling at the base level. At the start of the process a proposed order release plan
is generated by the first agent. Accordingly the agent from the base level performs a preliminary
scheduling of these orders and may report very expensive orders as feedback. This information is
then taken into consideration on the top level which adapts the order release plan accordingly. Here
the top level agent minimises the overall costs by load leveling on an aggregated model, while at
the bottom level the agent (mainly) minimises costs backorder costs.
%
Finally, although the introduced actions space reduction method, named \textit{independent agents},
works very well, it remains to be shown that the achievable policies are different to the ones for
agents without this adaption.

>>>>

\begin{abstract}
  % teilw. von IJPR paper uebernommen
  An essential task in manufacturing planning and control is to determine when to release orders to
  the shop floor. One key parameter is the lead time which is the planned time that elapses between
  the release of an order and its completion. Lead times are usually determined based on the
  measured duration orders take to traverse the production system, i.e.\@ the flow times.
  Traditional order release models assume static lead times, although it has been shown that they
  should be set dynamically to be able to react to the dynamic operational characteristics of
  production system. Therefore, we present an order release model which sets lead times dynamically
  by using an reinforcement learning approach. This algorithm is designed especially for
  applications with high variability and periodic feedback to the agent. Therefore, this paper aims
  at providing a proof-of-concept for the proposed algorithm. Therefore, we compare our method on a
  three-stage flow-shop simulation model not only to static order release techniques, but also to
  the commonly used deep Q-Learning algorithm. The results show that both reinforcement learning
  agents have room for improvement for queuing systems with low variability, that our proposed
  method usually outperforms deep Q-Learning and finally for systems with high variability that the
  proposed reinforcement learning algorithm performs very well, outperforming all other approaches.
  %
  % We use a  to compare the algorithm
  % to % and show that our approach outperforms
  % well-known order release mechanisms. We show that in the current version our proposed model using
  % reinforcement learning outperforms some, but not all other tested approaches.
  % EVTL: especially for scenarios with...
  \keywords{operations research, production planning, order release, machine learning, reinforcement
    learning}
\end{abstract}

@@

Therefore, in the future we plan to develop \ARA{} further to a actor-critic state-of-the-art
reinforcement learning algorithm. We hypothesise that due to the more correct state-action value
estimations of \ARA{} as compared to deep Q-Learning, cf. \citet{schneckenreither2020average}, the
critic will provide a better feedback of the value function update to the actor. This should lead to
better policies than with standard actor-critic algorithms, e.g. A3C~\citep{mnih2016asynchronous}.
%
Furthermore, one limitation of this proof-of-concept study is that due to the computational
complexity we restricted our scope to flow-shop production systems only. In subsequent studies we
plan to test the algorithms on job-shop queuing systems as well.
%
Additionally, we want to exploit hierarchical production
planning~\citep{schneeweibeta1995hierarchical} by implementing agents on different hierarchical
levels which can bargain with each other. For instance, one agent might be responsible for medium
term planning order release decision at the top level, while another agent concentrates on
short-term scheduling at the base level. At the start of the process a proposed order release plan
is generated by the first agent. Accordingly the agent from the base level performs a preliminary
scheduling of these orders and may report very expensive orders as feedback. This information is
then taken into consideration on the top level which adapts the order release plan accordingly. Here
the top level agent minimises the overall costs by load leveling on an aggregated model, while at
the bottom level the agent (mainly) minimises costs backorder costs.
%
Finally, although the introduced actions space reduction method, named \textit{independent agents},
works very well, it remains to be shown that the achievable policies are different to the ones for
agents without this adaption.
